Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?

### 2022-09-23 Paper.Rmd
discussion is comin

Negativity Bias Theorem and Prospect Theory had a strong support in the case of search goods. The regression results showed that the reviews which had low ratings and/or reviews which had more negative words in them were found to be more helpful on the average. Additionally, Perceived Helpfulness has a higher responsiveness to Review Length when a review has a low rating which means that people care more about negative cues than positive cues.

-   talk about positive sentiments and ratings and compare them

```{=html}
<!-- -->
```
-   mention the search goods as well.

@@

-   talk about the limitations as we go

>>>>

Negativity Bias Theorem and Prospect Theory had a strong support in the case of search goods. The regression results showed that the reviews which had low ratings and/or reviews which had more negative words in them were found to be more helpful on the average. Additionally, Perceived Helpfulness has higher responsiveness to Review Length when a review has a low rating. This means that people care more about negative cues than positive cues probably because they want to cut down potential certain losses. A similar result was reflected by the negative coefficient of the proportion of positive words in a review. This shows that reviews with positive sentiments doesn't have a strong diagnostic value for consumers. Nonetheless, the U-Shape of the Review Rating variable also suggests positivity bias [@hoorens2014]. An explanation to this could be that certain brands or products might be favored by some customers and these customers might selectively tend towards positively rated reviews and find them helpful just because they love the brand [@zhu2021]. The reason why there is a divergence between the "positively rated review" and "a review with positive sentiment" might be explained by this. A consumer who has brand or product inclinations wants to be persuaded to have the product so this particular consumer doesn't really care about what is written in the review, he might skim through positive reviews until he feels persuaded. Since a preference towards a brand is subjective it might be speculated that a strong brand could embed experience attributes into search goods. A similar notion was discussed by @mudambi2010 where they classified Apple iPod as an experience good. That is although an MP3 player such as iPod has many objective search attributes such as storage capacity and battery life, what makes this particular product preferable is the product image that was created by Apple.

-   you can discuss about the fluidity of search and exp attributes

A similar strong support for Negativity Bias can't be observed in the case of movies. Only evidence for Negativity Bias was the significant linear interaction term between Review Length and Review Rating. According to this result the U-Shaped function of Review Rating is only observable when Review Length is high enough. This is actually the case for search goods as well but the interaction term doesn't interfere with the sign of the other coefficients there. However, this is certain that as the review rating gets higher the review loses its diagnostic value for both for experience and search goods because the coefficient of the Review Length weakens. This means that potential buyers require more elaboration when a review is rated low. For experience goods, high rated reviews become more helpful on the average when reviews are short. This also might be a sign for positivity bias where people pay more attention to reviews which were aligned with their own feelings [@zhu2021]. Since experience attributes are naturally subjective it is logical to think that readers look for reviews that they agree.

Various reasons could be speculated about why the Hypothesis 5 and Hypothesis 6 didn't hold for experience goods.

-   subjectivity, emolex, heterogeneous opinions, row 10, show other works which are in line with your results,

@@

-   talk about the limitations as we go
-   talk about whatever we speculate we are omitting the readers buying motivation
